BioTime

### 2019-07-02 data-raw/biotime.Rmd
Filter biotime data not original data.

#some names have multiple matches (same ID but multiple scinames), have to pick one
## in this case all the duplicates have an accepted and a synonym, but there are some single matches that are just synonyms
## so we have to find duplicate ID's and then filter
alt_dupes <- syn_res %>%
  select(-taxonID) %>%
  filter(taxonRank == "species") %>%
  group_by(input) %>%
  filter(n() > 1)

@@

#Just get rid of those with duplicates, deal with them later
add_syn_res <- syn_res %>% 
  filter(!input %in% alt_dupes$input) %>% #excluding duplicate matched species
  select(id = acceptedNameUsageID, input, scientificName) %>%
  distinct() %>%
  left_join(data %>% select(-species, -genus), by = c("input" = "genus_species"), na_matches =  "never") %>%
  rename(matchingName = input) %>%
  ungroup()

biotime_data <- biotime_data %>% 
  filter(!matchingName %in% add_syn_res$matchingName) %>%
  distinct() %>%
  bind_rows(add_syn_res)

>>>>

#some names have multiple matches (same ID but multiple scinames), have to pick one
## in this case all the duplicates have an accepted and a synonym, but there are some single matches that are just synonyms
## so we have to find duplicate ID's and then filter
alt_dupes <- syn_res %>%
  select(-taxonID) %>%
  #filter(taxonRank == "species") %>%
  group_by(input) %>%
  filter(n() > 1)

@@

#Just get rid of those with duplicates, deal with them later
add_syn_res <- syn_res %>% 
  filter(!input %in% alt_dupes$input) %>% #excluding duplicate matched species
  select(id = acceptedNameUsageID, matchingName = input, scientificName) %>%
  distinct() %>%
  left_join(biotime_data%>% select(-c(id, scientificName)), by = "matchingName", na_matches =  "never") %>%
  ungroup() %>%
  distinct()

biotime_data <- biotime_data %>% 
  filter(!matchingName %in% add_syn_res$matchingName) %>%
  bind_rows(add_syn_res)
